---
title: "Arima_Model"
output:
  html_document:
    df_print: paged
---

# Load the dataset
```{r }
rm(list=ls())

library(tidyquant)
apple_data <- getSymbols(Symbols = "AAPL", src = "yahoo", from = "2000-01-01", 
                        to = Sys.Date(), auto.assign = FALSE)

apple_data <- Cl(apple_data)
```

# STOCK CHARTING

In order to begin analysing stock, here's the charting plus some technical indicators such as Simple Moving Average (20 and 100), Bollinger bands (20, sd = 1), Relative Strength Index (14 days), and Moving Average Convergence Divergence (12, 25) as the technical analysis before forecasting.
```{r}
chart_Series(apple_data, col = "black")
add_SMA(n = 100, on = 1, col = "red")
add_SMA(n = 20, on = 1, col = "black")
add_RSI(n = 14, maType = "SMA")
add_BBands(n = 20, maType = "SMA", sd = 1, on = -1)
add_MACD(fast = 12, slow = 25, signal = 9, maType = "SMA", histogram = TRUE)
```
# Checking whether data is Stationary or Not
```{r}

plot(apple_data)
```
# Transforming the data with Log

```{r}
plot(log(apple_data)) 
```

As the data has been log-transformed, we can clearly see that the series shows some upward and downward trend in a given time interval. 
The stock also consist of some volatility and swing. These are the signs that the stock price movement is non-stationary. 
Matter of fact, most of financial data is non-stationary (in which the mean, variance, autocorrelation, are not constant over time), but most of them follow random walk model with or without drift (RWM or RWD), 
This is due to the stock tend to having trend and inconstant variance and mean in a given period. Given that we can guess that its a random walk, which means the current value (price) is equal to its price at time (t - 1) plus a random shock (White Noise), 
hence we should difference the data with certain lag in order to fit ARIMA model as we’ll see later

# Checking the Autocorrelation and Partial Autocorrelation Function
This is where we check whether the current value is correlated to the past/yesterdays value.

```{r}
acf_apple = acf(apple_data, lag.max = 320)

pacf_apple=pacf(apple_data, lag.max = 320)
```


# Making the Data Stationary
```{r}
apple_data_diff= diff(log(apple_data), lag =1) # Adjusting the mean

apple_data_diff = na.locf(apple_data_diff, na.rm = TRUE,
                      fromLast = TRUE) # Replacing missing values

plot(apple_data_diff)
```
# Testing the Stationarity using Augmented Dickey Fuller Test.
Null Hypothesis = Non-Satationary
Alternative Hyp = Stationary

```{r}
library(tseries)
adf <- adf.test(apple_data, alternative = c("stationary", "explosive"), 
                k = 0)
adf
```
Hence as p-value>0.05, we cannot RJ null and conclude that our undifferentiated apple stock data is non-Stationary.
```{r}
adf <- adf.test(apple_data_diff, alternative = c("stationary", "explosive"), 
                k = 0)
adf
```
AS the p-value<0.05, we can reject null and conclude that our differentiated apple stock data is stationary.



# Plotting ACF and PACF Curves
```{r}
acf_apple  = acf(apple_data_diff) # Determining the value of autoregressive AR(P)

pacf_apple = pacf(apple_data_diff) # Determining the value of moving avg MA(p)
```



# Build the ARIMA Model
R provides simple and automatic way to generate appropriate ARIMA(p, d, q) model using auto.arima() function in forecast package with the smallest Akaike Information Criterion (AIC), Bayes Information Criterion (BIC).
Here we pass in our train data, difference (d = 1),stationary = TRUE
```{r}
library(forecast)
set.seed(100)
arima_model <- auto.arima(apple_data_diff, stationary = TRUE, ic = c("aicc", "aic", "bic"), 
                          trace = TRUE)

summary(arima_model)

checkresiduals(arima_model) ###diagnostic cheking
```

# Fitting the model and forecasting
```{r}
arima <- arima(apple_data_diff, order = c(5, 0, 0))
summary(arima)

forecast_apple <- forecast(arima, h = 365)
plot(forecast_apple)

checkresiduals(arima)
```
Here our forecast for 365 days ahead shows straight line. This is due to nature of arima forecasting tends to be mean reversion. 
The Ljung Box test shows that the model residuals are non-autocorrelated, suggesting there's no heterocedasticity problem and the model is good, otherwise we might consider GARCH model.

# Forecating for 2021
```{r}
arima1 = arima(log(apple_data[1:5030]), order=c(5,1,0))
summary(arima1)

forecast_1=forecast(arima1, h=365)
a = ts(log(apple_data))
forecast_1 %>% autoplot()+autolayer(a)
```

Here while forecasting apple stock prices from Jan 2021, our model was able to capture upward trend
of apple stock price which was displayed in the very first plot.




# Forecasting for 1st week of november
```{r}
arima1 = arima(log(apple_data[1:5494]), order=c(5,1,0))
summary(arima1)

forecast_1=forecast(arima1, h=7)
a = ts(log(apple_data))
forecast_1 %>% autoplot()+autolayer(a)
```