---
title: "Arima_Model"
output:
  html_document:
    df_print: paged
---

# Load the dataset
```{r }
rm(list=ls())

library(tidyquant)
google_data <- getSymbols(Symbols = "GOOGL", src = "yahoo", from = "2000-01-01", 
                        to = Sys.Date(), auto.assign = FALSE)

google_data <- Cl(google_data)
```

# STOCK CHARTING

In order to begin analysing stock, here's the charting plus some technical indicators such as Simple Moving Average (20 and 100), Bollinger bands (20, sd = 1), Relative Strength Index (14 days), and Moving Average Convergence Divergence (12, 25) as the technical analysis before forecasting.
```{r}
chart_Series(google_data, col = "black")
add_SMA(n = 100, on = 1, col = "red")
add_SMA(n = 20, on = 1, col = "black")
add_RSI(n = 14, maType = "SMA")
add_BBands(n = 20, maType = "SMA", sd = 1, on = -1)
add_MACD(fast = 12, slow = 25, signal = 9, maType = "SMA", histogram = TRUE)
```
# Checking whether data is Stationary or Not
```{r}

plot(google_data)
```
# Transforming the data with Log

```{r}
plot(log(google_data)) 
```

As the data has been log-transformed, we can clearly see that the series shows some upward and downward trend in a given time interval. 
Through out the year of Aug 2004 to April 2008, the stock showed upward trend, immediately after April it shows downward trend then rising continuously afterwards. 
The stock also consist of some volatility and swing. These are the signs that the stock price movement is non-stationary. 
Matter of fact, most of financial data is non-stationary (in which the mean, variance, autocorrelation, are not constant over time), but most of them follow random walk model with or without drift (RWM or RWD), 
This is due to the stock tend to having trend and inconstant variance and mean in a given period. Given that we can guess that its a random walk, which means the current value (price) is equal to its price at time (t - 1) plus a random shock (White Noise), 
hence we should difference the data with certain lag in order to fit ARIMA model as we’ll see later

# Checking the Autocorrelation and Partial Autocorrelation Function
This is where we check whether the current value is correlated to the past/yesterdays value.

```{r}
acf_google = acf(google_data, lag.max = 320)

pacf_google=pacf(google_data, lag.max = 320)
```

Given by the ACF correlogram, we can see that the data shows strong and significant autocorrelation up to lag 320. 
For the PACF, significant autocorrelations appear in lag 20, 25, 28 and then the autocorralation starts oscillating aroung the 0. 
This is the sign of certain trend, but we are unsure wether the data has seasonality or not, given that the PACF does not have any significant seasonal pattern. 
Therefore we conclude that Google stock price is non-stationary.

TO make our data stationary we should differenciate it to adjust the mean component i.e. all mean are equal

# Making the Data Stationary
```{r}
google_data_diff= diff(log(google_data), lag =1) # Adjusting the mean

google_data_diff = na.locf(google_data_diff, na.rm = TRUE,
                      fromLast = TRUE) # Replacing missing values

plot(google_data_diff)
```
# Testing the Stationarity using Augmented Dickey Fuller Test.
Null Hypothesis = Non-Satationary
Alternative Hyp = Stationary

```{r}
library(tseries)
adf <- adf.test(google_data, alternative = c("stationary", "explosive"), 
                k = 0)
adf
```
Hence as p-value>0.05, we cannot RJ null and conclude that our undifferentiated google stock data is non-Stationary.
```{r}
adf <- adf.test(google_data_diff, alternative = c("stationary", "explosive"), 
                k = 0)
adf
```
AS the p-value<0.05, we can reject null and conclude that our differenciated google stock data is stationary.



# Plotting ACF and PACF Curves
```{r}
acf_google  = acf(google_data_diff) # Determining the value of autoregressive AR(P)

pacf_google = pacf(google_data_diff) # Determining the value of moving avg MA(p)
```



# Build the ARIMA Model
R provides simple and automatic way to generate appropriate ARIMA(p, d, q) model using auto.arima() function in forecast package with the smallest Akaike Information Criterion (AIC), Bayes Information Criterion (BIC).
Here we pass in our train data, difference (d = 1),stationary = TRUE
```{r}
library(forecast)
set.seed(100)
arima_model <- auto.arima(google_data_diff, stationary = TRUE, ic = c("aicc", "aic", "bic"), 
                          trace = TRUE)

summary(arima_model)

checkresiduals(arima_model) ###diagnostic cheking
```

# Fitting the model and forecasting
```{r}
arima <- arima(google_data_diff, order = c(4, 0, 2))
summary(arima)

forecast_google <- forecast(arima, h = 365)
plot(forecast_google)

checkresiduals(arima)
```
Here our forecast for 365 days ahead shows straight line. This is due to nature of arima forecasting tends to be mean reversion. 
The Ljung Box test shows that the model residuals are non-autocorrelated, suggesting there's no heterocedasticity problem and the model is good, otherwise we might consider GARCH model.

# Forecasting for 2021
```{r}
arima1 = arima(log(google_data[1:3869]), order=c(4,1,2))
summary(arima1)

forecast_1=forecast(arima1, h=365)
a = ts(log(google_data))
forecast_1 %>% autoplot()+autolayer(a)
```

Here while forecasting Google stock prices from Jan 2021, our model was able to capture upward trend
of google stock price which was displayed in the very first plot.

# Learning Outcome:
Sometimes forecasting time series is difficult, in a way that the forecaster should have some specific domain knowledges and skill plus often times we could encounter model that seems appropriate but cannot capture the data movement, and vice versa. 
If arima does not yield good result, that means the data has some characteristic that arima could not capture. 
Hence we can try using other time series models such as VAR, GARCH (volatiliry clustering), or even the sophisticated Fourier transformation model, depends on the data characteristics. 
Thus forecasting should not be taken as a fixed result, but instead interative process until we can find the perfect model that could predict the movement of financial data.


# Forecasting for Nov 1st week
```{r}
arima1 = arima(log(google_data[1:4332]), order=c(4,1,2))
summary(arima1)

forecast_1=forecast(arima1, h=7)
a = ts(log(google_data))
forecast_1 %>% autoplot()+autolayer(a)
```

